Facilities, Equipment, and Other Resources at Indiana University

### 2016-11-30 proposal/fac.tex
done

\noindent There are substantial central computing resources offered by
the University: our cyberinfrastructure is rated in the top 10 in the
U.S, and includes the Big Red cluster (30 TeraFlops), the Quarry
cluster (9 TeraFlops, general-purpose Unix computing), and supports
TeraGrid, I-Light, and the Open Science Grid. Dr. Ortiz (Department of
Physics) and Dr. Sabry (School of Informatics and Computing) have
access to departmental license software, as well as access to most
electronic and hard copy journals through Indiana University
Libraries, and access to conference facilities for meetings.

@@

The School maintains 10 full time staff members dedicated to IT
infrastructure and facilities with the mission of enabling world class
research and instruction

>>>>

\noindent There are substantial central computing resources offered by
the University: our cyberinfrastructure is rated in the top 10 in the
U.S, and includes the Big Red cluster (30 TeraFlops), the Quarry
cluster (9 TeraFlops, general-purpose Unix computing), and supports
TeraGrid, I-Light, and the Open Science Grid. Dr. Ortiz (Department of
Physics) and Dr. Sabry and Dr. Hanson (School of Informatics and
Computing) have access to departmental license software, as well as
access to most electronic and hard copy journals through Indiana
University Libraries, and access to conference facilities for
meetings.

@@

The School maintains 10 full time staff members dedicated to IT
infrastructure and facilities with the mission of enabling world class
research and instruction.
